Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2021-10-12 paper-correlations.tex
Use more recent RevTex
Modify misleading line
Replace subcaption with subfigure

\documentclass[reprint,amsmath,amssymb,aps,pre]{revtex4-1}
% Latex
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% Xelatex
%\usepackage{polyglossia}
%\usepackage{fontspec}
%\setdefaultlanguage{english}
%\setmainfont{DejaVu Sans}
%\setsansfont{DejaVu Sans}
%\setmonofont{DejaVu Sans Mono}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subcaption}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=.3\textwidth]{images/corr.png}
  \caption[]{{\small WTF?}}
  \label{fig:functions}
\end{figure}

@@

\onecolumngrid
\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/l2-2d.png}
    \caption[]{{\small Lineal-path correlation function}}
    \label{fig:l2-2d}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/s2-2d.png}
    \caption[]{{\small Two-point correlation function}}
    \label{fig:s2-2d}
  \end{subfigure}
  \vskip\baselineskip
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/ss-2d.png}
    \caption[]{{\small Surface-surface correlation function}}
    \label{fig:ss-2d}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/sv-2d.png}
    \caption[]{{\small Surface-void correlation function}}
    \label{fig:sv-2d}
  \end{subfigure}
  \caption[]{\small A comparison of calculated values of $L_2(r)$, $S_2(r)$,
    $F_{ss}(r)$ and $F_{sv}(r)$ with theoretical values for overlapping disks.}
  \label{fig:2d}
\end{figure*}

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/l2-3d.png}
    \caption[]{{\small Lineal-path correlation function}}
    \label{fig:l2-3d}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/s2-3d.png}
    \caption[]{{\small Two-point correlation function}}
    \label{fig:s3-3d}
  \end{subfigure}
  \vskip\baselineskip
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/ss-3d.png}
    \caption[]{{\small Surface-surface correlation function}}
    \label{fig:ss-3d}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/sv-3d.png}
    \caption[]{{\small Surface-void correlation function}}
    \label{fig:sv-3d}
  \end{subfigure}
  \caption[]{\small A comparison of calculated values of $L_2(r)$, $S_2(r)$,
    $F_{ss}(r)$ and $F_{sv}(r)$ with theoretical values for overlapping balls.}
  \label{fig:3d}
\end{figure*}

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/ps-2d.png}
    \caption[]{{\small Pore size correlation function (2D)}}
    \label{fig:ps-2d}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/cl-2d.png}
    \caption[]{{\small Chord length correlation function (2D)}}
    \label{fig:cl-2d}
  \end{subfigure}
  \vskip\baselineskip
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/ps-3d.png}
    \caption[]{{\small Pore size correlation function (3D)}}
    \label{fig:ps-3d}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/cl-3d.png}
    \caption[]{{\small Chord length correlation function (3D)}}
    \label{fig:cl-3d}
  \end{subfigure}
  \caption[]{\small A comparison of calculated values of $P(r)$ and $p(r)$
    with theoretical values for overlapping disks (\cref{fig:ps-2d} and
    \cref{fig:cl-2d}) and balls(\cref{fig:ps-3d} and \cref{fig:cl-3d}).}
  \label{fig:pscl}
\end{figure*}
\twocolumngrid

\section{Efficiency of our algorithms}
\label{effisec}
To measure efficiecy of our algorithms we use a machine with the following
configuration:
\begin{itemize}
\item \textbf{CPU}: AMD Ryzen 5 1600X running at 2200~MHz
\item \textbf{Memory}: 32~Gb DDR4-2400 memory
\item \textbf{GPU}: Nvidia Tesla V100 with 32~Gb video memory
\end{itemize}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=.3\textwidth]{images/timing-image.png}
  \caption[]{{\small An example of 2D image used in timing measurements}}
  \label{fig:valuenoise}
\end{figure}

\onecolumngrid
\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-2d.png}
    \caption[]{{\small Two-dimensional case, module \code{Directional}}}
    \label{fig:timings-2d}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-3d.png}
    \caption[]{{\small Three-dimensional case, module \code{Directional}}}
    \label{fig:timings-3d}
  \end{subfigure}
  \vskip\baselineskip
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-2d-map.png}
    \caption[]{{\small Two-dimensional case, module \code{Map}, CPU}}
    \label{fig:timings-2d-map}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-3d-map.png}
    \caption[]{{\small Three-dimensional case, module \code{Map}, CPU}}
    \label{fig:timings-3d-map}
  \end{subfigure}
  \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-2d-gpu.png}
    \caption[]{{\small Two-dimensional case, module \code{Map}, GPU}}
    \label{fig:timings-2d-gpu}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-3d-gpu.png}
    \caption[]{{\small Three-dimensional case, module \code{Map}, GPU}}
    \label{fig:timings-3d-gpu}
  \end{subfigure}
  \caption[]{\small Execution times for different correlation functions.}
  \label{fig:timings}
\end{figure*}
\twocolumngrid

>>>>

\documentclass[reprint,amsmath,amssymb,aps,pre]{revtex4-1}
% Latex
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% Xelatex
%\usepackage{polyglossia}
%\usepackage{fontspec}
%\setdefaultlanguage{english}
%\setmainfont{DejaVu Sans}
%\setsansfont{DejaVu Sans}
%\setmonofont{DejaVu Sans Mono}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.9\linewidth]{images/corr.png}
  \caption[]{WTF?}
  \label{fig:functions}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \subfigure[Lineal-path correlation function]{
    \includegraphics[width=0.475\linewidth]{images/l2-2d.png}
    \label{fig:l2-2d}}
  \hfill
  \subfigure[Two-point correlation function]{
    \includegraphics[width=0.475\linewidth]{images/s2-2d.png}
    \label{fig:s2-2d}}
  \vskip\baselineskip
  \subfigure[Surface-surface correlation function]{
    \includegraphics[width=0.475\linewidth]{images/ss-2d.png}
    \label{fig:ss-2d}}
  \hfill
  \subfigure[Surface-void correlation function]{
    \includegraphics[width=0.475\linewidth]{images/sv-2d.png}
    \label{fig:sv-2d}}
  \caption[]{A comparison of calculated values of $L_2(r)$, $S_2(r)$,
    $F_{ss}(r)$ and $F_{sv}(r)$ with theoretical values for overlapping disks.}
  \label{fig:2d}
\end{figure*}

\begin{figure*}[t]
  \centering
  \subfigure[Lineal-path correlation function]{
    \includegraphics[width=0.475\linewidth]{images/l2-3d.png}
    \label{fig:l2-3d}}
  \hfill
  \subfigure[Two-point correlation function]{
    \includegraphics[width=0.475\linewidth]{images/s2-3d.png}
    \label{fig:s3-3d}}
  \vskip\baselineskip
  \subfigure[Surface-surface correlation function]{
    \includegraphics[width=0.475\linewidth]{images/ss-3d.png}
    \label{fig:ss-3d}}
  \hfill
  \subfigure[Surface-void correlation function]{
    \includegraphics[width=0.475\linewidth]{images/sv-3d.png}
    \label{fig:sv-3d}}
  \caption[]{A comparison of calculated values of $L_2(r)$, $S_2(r)$,
    $F_{ss}(r)$ and $F_{sv}(r)$ with theoretical values for overlapping balls.}
  \label{fig:3d}
\end{figure*}

\begin{figure*}[t]
  \centering
  \subfigure[Pore size correlation function (2D)]{
    \includegraphics[width=0.475\linewidth]{images/ps-2d.png}
    \label{fig:ps-2d}}
  \hfill
  \subfigure[Chord length correlation function (2D)]{
    \includegraphics[width=0.475\linewidth]{images/cl-2d.png}
    \label{fig:cl-2d}}
  \vskip\baselineskip
  \subfigure[Pore size correlation function (3D)]{
    \includegraphics[width=0.475\linewidth]{images/ps-3d.png}
    \label{fig:ps-3d}}
  \hfill
  \subfigure[Chord length correlation function (3D)]{
    \includegraphics[width=0.475\linewidth]{images/cl-3d.png}
    \label{fig:cl-3d}}
  \caption[]{A comparison of calculated values of $P(r)$ and $p(r)$
    with theoretical values for overlapping disks (\cref{fig:ps-2d} and
    \cref{fig:cl-2d}) and balls(\cref{fig:ps-3d} and \cref{fig:cl-3d}).}
  \label{fig:pscl}
\end{figure*}

\section{Efficiency of our algorithms}
\label{effisec}
To measure efficiecy of our algorithms we use a machine with the following
configuration:
\begin{itemize}
\item \textbf{CPU}: AMD Ryzen 5 1600X
\item \textbf{Memory}: 32~Gb DDR4-2400 memory
\item \textbf{GPU}: Nvidia Tesla V100 with 32~Gb video memory
\end{itemize}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.9\linewidth]{images/timing-image.png}
  \caption[]{An example of 2D image used in timing measurements.}
  \label{fig:valuenoise}
\end{figure}

\begin{figure*}[t]
  \centering
  \subfigure[Two-dimensional case, module \code{Directional}]{
    \includegraphics[width=0.475\linewidth]{images/time-2d.png}
    \label{fig:timings-2d}}
  \hfill
  \subfigure[Three-dimensional case, module \code{Directional}]{
    \includegraphics[width=0.475\linewidth]{images/time-3d.png}
    \label{fig:timings-3d}}
  \vskip\baselineskip
  \subfigure[Two-dimensional case, module \code{Map}, CPU]{
    \includegraphics[width=0.475\linewidth]{images/time-2d-map.png}
    \label{fig:timings-2d-map}}
  \hfill
  \subfigure[Three-dimensional case, module \code{Map}, CPU]{
    \includegraphics[width=0.475\linewidth]{images/time-3d-map.png}
    \label{fig:timings-3d-map}}
  \vskip\baselineskip
  \subfigure[Two-dimensional case, module \code{Map}, GPU]{
    \includegraphics[width=0.475\linewidth]{images/time-2d-gpu.png}
    \label{fig:timings-2d-gpu}}
  \hfill
  \subfigure[Three-dimensional case, module \code{Map}, GPU]{
    \includegraphics[width=0.475\linewidth]{images/time-3d-gpu.png}
    \label{fig:timings-3d-gpu}}
  \caption[]{Execution times for different correlation functions.}
  \label{fig:timings}
\end{figure*}
